### 2015-06-28 reports/paper/experiment.tex
update

\textcolor{red}{To test how sensitive the color change is to the different volumes in our system, we have conducted the following experiment. In this experiment, we moved the acoustic source clockwise in an elliptical fashion. As we are moving the source, we varied the source volume gradually and noted its color change. We started with the volume set to the maximum (the corresponding color is red). Then we gradually decreased the volume as the move to the right. After the volume is decreased to $60\%$ of the maximum, we started to gradually increase the volume until the maximum is reached again. Figure~\ref{fig:show_color_3} gives a visual presentation of the painted result. As can be seen from the figure, the top left region of the drawn ellipse is red. The color then gradually changes to the green yellow range and then back to the red orange range as we complete the ellipse. A video demonstration of this experiment is available at~\cite{demo:color3} }

>>>>

To test how sensitive the color change is to the different volumes in our system, we have conducted the following experiment. In this experiment, we moved the acoustic source clockwise in an elliptical fashion. As we are moving the source, we varied the source volume gradually and noted its color change. We started with the volume set to the maximum (the corresponding color is red). Then we gradually decreased the volume as the move to the right. After the volume is decreased to $60\%$ of the maximum, we started to gradually increase the volume until the maximum is reached again. Figure~\ref{fig:show_color_3} gives a visual presentation of the painted result. As can be seen from the figure, the top left region of the drawn ellipse is red. The color then gradually changes to the green yellow range and then back to the red orange range as we complete the ellipse. A video demonstration of this experiment is available at~\cite{demo:color3}.
